---
title: "Skate Metrics"
author: "Brandon"
date: "10/22/2021"
output: html_document
---

# Importing and restructuring the data

```{r}
# Handle NA strings: https://stackoverflow.com/questions/24172111/change-the-blank-cells-to-na#24172277
data <-
  read.csv(file = 'Skate Metrics.csv', na.strings = c("", " ", "NA"))
head(data)

library(tidyr)
library(data.table)
library(lubridate)
str(data)

# as.Date : https://stackoverflow.com/questions/47230146/error-message-do-not-know-how-to-convert-dataframecol-to-class-date?rq=1
data$Date <- as.Date(data$Date, format = "%m/%d/%Y")

# Filling downward the Date and Trick column's values
# - This assumes we didn't manually fill them in for the same Date or Trick
data <- fill(data, c("Date", "Trick"), .direction = "down")

## Formatting the dates nicely
### I'm second-guessing whether I need these in the general dataset;
### maybe change to only using these functions when I'll actually need the formatted dates.
# data$Week <- week(data$Date)
# data$Month <- month(data$Date)
# data$Year <- year(data$Date)
# data$MonthYear <- my(data$Date)

# Prior probability from the existing Bet / Odds data
# It handles NA data perfectly!
data$PriorProbability <- (data$Bet.Succeed / (data$Bet.Succeed + data$Bet.Fail))
```

# Writing the restructured data to a CSV file

```{r}
write.csv(data,
          "Skate Metrics - Base Data.csv",
          row.names = FALSE,
          quote = FALSE)
```

# Working with the data

## Summarizing by Trick and various stats

```{r}
df = as.data.table(data)

# Order: https://stackoverflow.com/questions/12353820/sort-rows-in-data-table-in-decreasing-order-on-string-key-order-x-v-gives-er
data2 <-
  df[, .("Hits to Attempts Ratio" = sum(Outcome) / length(Outcome), "Times Landed" = sum(Outcome), "Num of Attempts" = length(Outcome)), by =
       c("Trick")][order(-`Hits to Attempts Ratio`)]
colnames(data2) # [1] "Trick" "V1"    "V2"    "V3"

# data2[,c(1:3,5)]

data2

# Number of days of tricks recorded
length(unique(data$Date))

# Number of attempts in dataset
sum(data2[, 4])

# Nollie attempts before July 20, 2020
first_period_nollie <-
  df[Trick == "Nollie" &
       Date < "20-07-20", .(a = sum(Outcome), b = length(Outcome) - sum(Outcome))]
second_period_nollie <-
  df[Trick == "Nollie" &
       Date >= "20-07-20", .(a = sum(Outcome), b = length(Outcome) - sum(Outcome))]

### Not really sure what all this does
# : https://stackoverflow.com/questions/2564258/plot-two-graphs-in-same-plot-in-r/19039094#19039094

library(ggplot2)
library(reshape2)

# original data in a 'wide' format
x <- seq(0, 1, length = 100)
y1 <- dbeta(x, first_period_nollie$a, first_period_nollie$b)
y2 <- dbeta(x, second_period_nollie$a, second_period_nollie$b)
dff <- data.frame(x, first_period = y1, second_period = y2)

# melt the data to a long format
df2 <- melt(data = dff, id.vars = "x")

# plot, using the aesthetics argument 'colour'
ggplot(data = df2, aes(x = x, y = value, colour = variable)) + geom_line()

# qbeta(0.025,first_period_nollie$a,first_period_nollie$b)
# qbeta(0.975,first_period_nollie$a,first_period_nollie$b)
```

### Writing this data to a CSV
```{r}
write.csv(data2,
          "Trick Hits to Attempts.csv",
          row.names = FALSE,
          quote = FALSE) # write summary to csv file
```


## Making a posterior distribution

* Convert average to nearest 1/N
  * Use the round_any function mentioned here https://stackoverflow.com/a/56455926
* Get the fraction for this - use the numerator and the denominator to get `a` and `b` for the beta dist from `a = numerator` and `b = denominator - numerator` - and plug those into the beta function to produce the posterior dist (we can aggregate the outcomes to make the `a` and `b` values)
  * Use the package `fractional` to work with the fractions: https://rdrr.io/cran/fractional/man/numerators.html


```{r}
library(lubridate)
df = as.data.table(data)

df$Week <- week(df$Date)
df$Month <- month(df$Date)
df$Year <- year(df$Date)

df$MonthYear <- paste(df$Month, df$Year, sep = "-")

# Sort data in reverse chronological order, so that we can group MonthYear in the best order
# TODO: Figure out if this is even the order that I'd need for charts
#   We might just need chronological order.
df <- df[,,][order(-Date)]

# Average the prior probability column by Trick and time periods (NAs are excluded)
## Order: https://stackoverflow.com/questions/12353820/sort-rows-in-data-table-in-decreasing-order-on-string-key-order-x-v-gives-er
data2 <-
  df[, .("Times Landed" = sum(Outcome), "Times Not Landed" = (length(Outcome) - sum(Outcome)), "Num of Attempts" = length(Outcome), "Average Prior Probability" = mean(PriorProbability, na.rm = TRUE)), by =
       c("Trick","MonthYear")]

## TODO: Handle cases where a trick hasn't had any successes (within time period)
### This might defer to priors; downstream data visualizations should make it apparent if a distribution is purely composed of priors
## TODO: Handle cases where a trick hasn't had any prior data provided
### Currently R gives these tricks a NaN value when we try to average them
## TODO: Handle case where a trick has neither prior data nor successes

# Convert average to nearest 1/N (which I assume can be rounded turned into a fraction easily)
# TODO: Use the round_any function mentioned here https://stackoverflow.com/a/56455926
## If I can't find a way to round a number to the nearest (1/N), then I may need to keep N as 10 for now, which `round(0.55, digits = 1)` would assume
# prior_N <- 10

## Get fraction for a value
library(fractional)
fractional(0.25)

## TODO: Apply this function to the Average Prior Probability, extract numerator and denominator

# Get the fraction for this - use the numerator and the denominator to get `a` and `b` for the beta dist from `a = numerator` and `b = denominator - numerator` - and plug those into the beta function to produce the posterior dist (we can aggregate the outcomes to make the `a` and `b` values)

```

